cvx-flats

### 2020-04-23 neurips-20/cvx-flats.tex
Statements for finite case added.

\section{Finite outcome settings and finite properties}\label{sec:finite-calib}
\begin{definition}[Calibrated]
	Let $\ell : \R \times \Y \to \reals_+$ be a discrete loss eliciting the property $\gamma$.
	A surrogate loss $L : \reals^d \times \Y \to \reals_+$ is \emph{calibrated} with respect to $\ell$ if there exists a link function $\psi: \reals^d \to \R$ such that
	\begin{equation}
	\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.~
	\end{equation}
\end{definition}

\cite{ramaswamy2016convex} introduces \emph{Convex Calibration Dimension}, which studies the minimal dimension input $d$ to construct a convex surrogate $L : \reals^d \times \Y \to \reals_+$ that is calibrated with respect to a given discrete loss $\ell$.

@@

@@

The following is a statement from~\cite{ramaswamy2016convex} providing an upper bound on the convex calibration dimension of a given discrete loss.
However, using tools from property elicitation, we can simplify their proof, which relies on considering sequences of losses that approach the infimum and taking $\epsilon$-subdifferentials of the surrogate loss.

\begin{theorem}[\cite{ramaswamy2016convex}]
	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
	Take $p \in \simplex$ and $r \in \R$ such that $p \in \gamma_r$.
	Then \jessie{Need to define FSD $\mu_{\gamma_r}$}
	\begin{equation}
	\ccdim(\ell) \geq \|p\|_0 - \mu_{\gamma_r}(p) - 1~.~
	\end{equation}
\end{theorem}
\begin{proof}
	\jessie{Abbreviated FSD proof}
\end{proof}

>>>>

\section{Finite report and outcome settings}\label{sec:finite-calib}
\jessie{Note subtle difference between calib and consistent, but formally introduce calibration.}
\begin{definition}[Calibrated]
	Let $\ell : \R \times \Y \to \reals_+$ be a discrete loss eliciting the property $\gamma$.
	A surrogate loss $L : \reals^d \times \Y \to \reals_+$ is \emph{calibrated} with respect to $\ell$ if there exists a link function $\psi: \reals^d \to \R$ such that
	\begin{equation}
	\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.~
	\end{equation}
\end{definition}

\jessie{Thankfully, \cite{ramaswamy2016convex} has swooped in to save the day with below result. (Original for binary and multiclass classification come from~\cite{bartlett2006convexity} and \cite{tewari2007consistency}, respectively.)}

@@

\hrule 
\bigskip

\begin{lemma}
	Suppose we are given a discrete loss $\ell : \R \times\Y \to \reals_+$ eliciting the property $\gamma$.
	If $(L, \psi)$ is calibrated with respect to $\ell$, then $L$ indirectly elicits $\gamma$.
\end{lemma}
The proof follows from observing that Theorem~\ref{thm:calib-iff-consistent} yields consistency of $(L,\psi)$ with respect to $\ell$ from calibration, then applying Proposition~\ref{prop:consistent-implies-indir-elic}.

\iffalse
\begin{lemma}
  If a convex loss $L:\reals^d \times\Y \to \reals$ with $|\Y| < \infty$ indirectly elicits a finite property $\gamma$, then for all $p \in \simplex$ and $r \in \gamma(p)$, there is a flat $F$ containing $p$ that is $(n-d-1)$-dimensional such that $F \cap \simplex \subseteq \gamma_r$.
\end{lemma}
This is the contrapositive of Theorem~\ref{thm:cvx-flats}, and what is actually proven there.
\fi

\jessie{Ramaswamy et al introduce FSD as a technique to provide their lower bound...}
\begin{definition}[Feasible subspace dimension]
	The \emph{Feasible Subspace Dimension} of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$, denoted by $\mu_\C(p)$ is defined as the dimension of the subspace $\F_\C(p) \cap (-\F_\C(p))$, where $\F_\C(p)$ is the cone of feasible directions of $\C$ at $p$\footnote{The cone of feasible directions is given by $\F_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 \geq 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (0,\epsilon_0) \}$}.
\end{definition}
\jessiet{This is the definition from the Ramaswamy paper, but I have a small qualm with this definition... it should be fine if $\C$ is a polytope, but if $\C$ is not a polytope, it's unclear what they want from this definition.  For finite elicitable properties, obviously this doesn't matter, but yeah...}
\jessiet{I also can't tell if this is a small bug on their end, but I think they define the cone of feasible directions as the open cone, but they really want the closed cone.  I think?}

\begin{lemma}\label{lem:feas-sub-is-a-flat}
	Suppose we have the finite property $\gamma$ indirectly elicited by the convex loss $L : \reals^d \times \Y \to \reals$ and distribution $p \in \simplex$.
	The subspace $F := \F_\C(p) \cap (-\F_\C(p))$ is a flat of the loss $L$, contains $p$, and $F \cap \simplex \subseteq \gamma_r$.
\end{lemma}
\begin{proof}
	\jessie{TODO}
\end{proof}

\iffalse
\begin{remark}
	Suppose we are given a finite property $\gamma$ and distribution $p \in \simplex$.
	If $L :\reals^d \times\Y \to \reals$ indirectly elicits $\gamma$, then
	For all $r \in \gamma(p)$, we have 
	\begin{equation}
	\mu_{\gamma_r}(p) \leq f(p)~,~
	\end{equation}
	where $f(p)$ is the maximal dimension of a flat $F$ of $L$ containing $p$ such that $F \cap \simplex \subseteq \gamma_r$. 
\end{remark}
\fi

The following is a statement from~\cite{ramaswamy2016convex} providing an upper bound on the convex calibration dimension of a given discrete loss, which now follows as a Corollary of our Theorem~\ref{thm:cvx-flats} and Lemma~\ref{lem:feas-sub-is-a-flat}.

\begin{corollary}[\cite{ramaswamy2016convex}]
	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
	Take $p \in \simplex$ and $r \in \R$ such that $p \in \gamma_r$.
	\begin{equation}
	\ccdim(\ell) \geq \|p\|_0 - \mu_{\gamma_r}(p) - 1~.~
	\end{equation}
\end{corollary}

\jessie{Don't worry about this for now.}
\subsection{Elicitation complexity and convex calibration dimension}
\cite{ramaswamy2016convex} introduces \emph{Convex Calibration Dimension}, which studies the minimal dimension input $d$ to construct a convex surrogate $L : \reals^d \times \Y \to \reals_+$ that is calibrated with respect to a given discrete loss $\ell$, and is similar to elicitaiton complexity as introduced in Definition~\ref{def:elic:cplx}.

@@
